Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-02-16 202010_jslhr/paper.Rmd
for proofing

# #up to 3 keywords
# keywords          : "reliability; validation; daylong audiorecordings; citizen science; Zooniverse; LENA; long-form recordings"
# wordcount         : "7,113"

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
lineno            : yes

@@

@@

#document session info

sink("lastknit_session_info.txt")
sessionInfo()
sink()
```

@@

@@

# create lab column with easier to read correspondance
data_all$lab<-as.character(data_all$Major_Choice)
data_all$lab[data_all$lab=="Non-canonical syllables"]<-"Non-Canonical"
data_all$lab[data_all$lab=="Canonical syllables"]<-"Canonical"
data_all$lab[data_all$lab %in% c("Don't mark","None")]<-"Junk"
data_all$lab=factor(data_all$lab,levels=levels(data_all$Zoon_classif))
#apply same factor levels as zooniverse so that we can do symmetrical confusion matrices

@@

### Data post-processing
<!-- ac this section still has numbers typed in  -->

An impressive total of `r x["nusers","x"]` individual Zooniverse users provided `r x["njudgments","x"]` judgments on `r x["nchunks","x"]` 500-ms chunks, corresponding to `r dim(data_all)[1]` 11,980 LENA^TM^ segments. For a variety of technical mishaps, XX chunks had to be excluded, leading to `r length(levels(factor(chunks$subject_id)))` chunks and `r length(levels(factor(data_all$segmentId_DB)))` LENA^TM^ segments for which we had five Zooniverse labels. Among these, `r round(sum(chunks$nvotes<2)/dim(chunks)[1]*100,1)`% had no matching labels, `r round(sum(chunks$nvotes==2)/dim(chunks)[1]*100,1)`% had two matching labels (the threshold used for lab-annotated segments), and `r round(sum(chunks$nvotes>=3)/dim(chunks)[1]*100,1)`% had three or more matching labels, or majority agreement. Future work may explore different ways of setting the minimal requirement for convergence, but for further analyses here, we focused on the `r round(sum(chunks$nvotes>=3)/dim(chunks)[1]*100,1)`%  of chunks that *did* have at least three labels in agreement (i.e., majority agreement). This represented `r sum(chunks$nvotes>=3)*5` 135,725 labels for `r sum(chunks$nvotes>=3)` 27,145 chunks, corresponding to `r dim(data_all)[1]` LENA^TM^ segments. Given that each chunk is 500 ms in length, this means about `r (sum(chunks$nvotes>=3)*.5)/60/60` hours of audio data were annotated by 8 different annotators (3 in the laboratory, 5 on Zooniverse).

@@

Lab annotators provided judgments at the level of LENA^TM^ segments, whereas Zooniverse annotators provided judgments on 500 ms chunks, which are typically smaller than the segments. Therefore, we needed to combine chunk-level judgments to reconstruct segment-level judgments.

We did this by considering the majority label extracted from Zooniverse judgments for all chunks associated with each segment, and then following these rules: If the majority label for all chunks associated with a given segment were Junk, then the segment was labelled as Junk; then, following a hierarchy (Canonical>Non-canonical>Crying>Laughing), segments with at least one instance of each judgment were labelled as such:

@@

#and reset the factors for cleanliness
data_all$Zoon_classif=factor(data_all$Zoon_classif)
data_all$lab=factor(data_all$lab)
sample_data<-cbind(data_all$lab,data_all$Zoon_classif)

@@

The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, especially in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was [`r printp(min(resampling$lp_r_all))`,`r printp(max(resampling$lp_r_all))`]; for the Angelman syndrome group [`r printp(min(resampling$lp_r_as))`,`r printp(max(resampling$lp_r_as))`]; for the low-risk group [`r printp(min(resampling$lp_r_lr))`,`r printp(max(resampling$lp_r_lr))`].  For Canonical Proportion, the range of correlations found for all infants was [`r printp(min(resampling$cp_r_all))`,`r printp(max(resampling$cp_r_all))`]; for the Angelman syndrome group [`r printp(min(resampling$cp_r_as))`,`r printp(max(resampling$cp_r_as))`]; for the low-risk group [`r printp(min(resampling$cp_r_lr))`,`r printp(max(resampling$cp_r_lr))`].

>>>>

# #up to 3 keywords
# keywords          : "reliability; validation; daylong audiorecordings; citizen science; Zooniverse; LENA; long-form recordings"
# wordcount         : "9375"

@@

figsintext        : no
figurelist        : yes
tablelist         : no
footnotelist      : no
lineno            : no

@@

#document session info
capture.output(sessionInfo(),file="lastknit_session_info.txt")

@@

@@

label_options=c("Canonical"   ,     "Crying"  ,        "Junk"  ,    "Laughing", "Non-Canonical")

@@

# create lab column with easier to read correspondance
data_all$lab<-as.character(data_all$Major_Choice)
data_all$lab[data_all$lab=="Non-canonical syllables"]<-"Non-Canonical"
data_all$lab[data_all$lab=="Canonical syllables"]<-"Canonical"
data_all$lab[data_all$lab %in% c("Don't mark","None")]<-"Junk"
data_all$lab=factor(data_all$lab,levels=label_options)
#apply same factor levels as zooniverse so that we can do symmetrical confusion matrices

@@

### Data post-processing

The following description uses several key concepts: A "judgment" or "label" is a single classification provided by a Zooniverse user in response to a single chunk; a "chunk" is a 500-ms clip extracted from the daylong audio to represent part or all of a segment; a segment is a section of the daylong audio automatically classified as having been uttered by the key child according to the LENA^TM^ algorithm. Bearing this terminology in mind, we provide an overview of the data and how it was processed before the analyses below.

An impressive total of `r prettyNum(x["nusers","x"],big.mark=",")` individual Zooniverse users provided `r prettyNum(x["njudgments","x"],big.mark=",")` judgments on `r prettyNum(x["nchunks","x"],big.mark=",")` 500-ms chunks, corresponding to `r prettyNum(dim(data_all)[1],big.mark=",")` LENA^TM^ segments. For a variety of technical mishaps, `r prettyNum((x["njudgments","x"] - dim(chunks)[1]*5),big.mark=",")` judgments had to be excluded, leaving `r prettyNum(length(levels(factor(chunks$filename))),big.mark=",")` chunks (from `r prettyNum(length(levels(factor(data_all$segmentId_DB))),big.mark=",")` LENA^TM^ segments) for which we had five Zooniverse labels (for a total of `r prettyNum(dim(chunks)[1]*5,big.mark=",")` judgments included). Among these `r prettyNum(length(levels(factor(chunks$filename))),big.mark=",")` chunks, `r round(sum(chunks$nvotes<2)/dim(chunks)[1]*100,2)`% had no matching labels, `r round(sum(chunks$nvotes==2)/dim(chunks)[1]*100,2)`% had two matching labels (the threshold used for lab-annotated segments), and `r round(sum(chunks$nvotes>=3)/dim(chunks)[1]*100,2)`% had three or more matching labels, or majority agreement within Zooniverse labels. Future work may explore different ways of setting the minimal requirement for convergence, but for further analyses here, we focused on the `r round(sum(chunks$nvotes>=3)/dim(chunks)[1]*100,2)`%  of chunks that *did* have at least three labels in agreement (i.e., majority agreement). This represented `r prettyNum(sum(chunks$nvotes>=3)*5,big.mark=",")` labels for `r prettyNum(sum(chunks$nvotes>=3),big.mark=",")` chunks, corresponding to `r prettyNum(dim(data_all)[1],big.mark=",")` LENA^TM^ segments. Given that each chunk is 500 ms in length, this means about `r (sum(chunks$nvotes>=3)*.5)/60/60` hours of audio data were annotated by 8 different annotators (3 in the laboratory, 5 on Zooniverse).

@@

There was one more layer of pre-processing that was necessary for our analyses: Lab annotators provided judgments at the level of LENA^TM^ segments, whereas Zooniverse annotators provided judgments on 500 ms chunks, which are typically smaller than the segments. Therefore, we needed to combine chunk-level judgments to reconstruct segment-level judgments. We did this by considering the majority label extracted from Zooniverse judgments for all chunks associated with each segment, and then following these rules: If the majority label for all chunks associated with a given segment were Junk, then the segment was labelled as Junk; then, following a hierarchy (Canonical>Non-canonical>Crying>Laughing), segments with at least one instance of each judgment were labelled as such:

@@

# remove non-majority labels from zooniverse
data_all[data_all$Zoon_classif %in% label_options,]->data_all

#and reset the factors for cleanliness
data_all$Zoon_classif=factor(data_all$Zoon_classif, levels=label_options)
data_all$lab=factor(data_all$lab, levels=label_options)
sample_data<-cbind(data_all$lab,data_all$Zoon_classif)

@@

The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, especially in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was [`r printr(min(resampling$lp_r_all))`,`r printr(max(resampling$lp_r_all))`]; for the Angelman syndrome group [`r printr(min(resampling$lp_r_as))`,`r printr(max(resampling$lp_r_as))`]; for the low-risk group [`r printr(min(resampling$lp_r_lr))`,`r printr(max(resampling$lp_r_lr))`].  For Canonical Proportion, the range of correlations found for all infants was [`r printr(min(resampling$cp_r_all))`,`r printr(max(resampling$cp_r_all))`]; for the Angelman syndrome group [`r printr(min(resampling$cp_r_as))`,`r printr(max(resampling$cp_r_as))`]; for the low-risk group [`r printr(min(resampling$cp_r_lr))`,`r printr(max(resampling$cp_r_lr))`].

### 2021-02-16 202010_jslhr/paper.tex
for proofing

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29 rue d'Ulm, 75005, Paris, France. E-mail: alecristia@gmail.com}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\singlespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

@@

A large body of research has investigated both fine-grained and coarse descriptions of children's vocalizations as a function of age and diagnosis, and it is beyond the scope of this paper to provide a full summary of this work {[}but see \textbf{XX ADD REFERENCE} for a recent summary{]}. Moreover, the way in which vocal development has been studied in the past may not easily translate to long-form recordings. As mentioned earlier, long-form recordings have several advantages, including capturing the child's vocal patterns in their natural environment and being able to accumulate a great amount of data easily, which is particularly useful for diagnoses and pathologies characterized by low levels of vocal production. However, this also means that the audiorecording is harder to process than an audiorecording gathered in more manicured and stable conditions: In a typical daylong recording, the child will sometimes be in a quiet room with just her primary caregiver, but later in a noisy supermarket or having dinner with family and friends. In fact, human annotation of such audio is estimated to take about 30 times the audio length, with these estimates being greater the more precise one wants or needs to be (Casillas et al., 2017). It is for this reason that most users of long-form recordings have turned to automatized software for at least a first-pass analysis.

@@

An impressive total of 4,825 individual Zooniverse users provided labels for the Maturity of Baby Sounds project, of which the present data set is one part. For this project, we collected a total of 169,767 judgments provided for 33,731 500-ms chunks, corresponding to 11,980 LENA\textsuperscript{TM} segments. Nearly a fifth of chunks did not have at least 3 labels in agreement out of the 5 Zooniverse labels (N = 6,585, 19\% of all chunks). Of the chunks without a majority agreement, 4341 (66\%) contained one or two Junk judgments (out of 5), 6523 (99,9\%) had at least two matching judgments (the threshold used for lab-annotated segments), and only 61 (0,01\%) had 5 different judgments. Future work may explore different ways of setting the minimal requirement for convergence, but for further analyses here, we focused on the 81\% of chunks that did have at least 3 labels in agreement; this represented 135,725 labels for 27,145 chunks, corresponding to 11,593 LENA\textsuperscript{TM} segments. As the segments average 1.12 seconds in length, this means about 3.8 hours of audio data were annotated by 8 different annotators (3 in the laboratory, 5 on Zooniverse).

Lab annotators provided judgments at the level of LENA\textsuperscript{TM} segments, whereas Zooniverse annotators provided judgments on 500 ms chunks, which are typically smaller than the segments. Therefore, we needed to combine chunk-level judgments to reconstruct segment-level judgments.

We did this by considering the majority label extracted from Zooniverse judgments for all chunks associated with each segment, and then following these rules: If the majority label for all chunks associated with a given segment were Junk, then the segment was labelled as Junk; then, following a hierarchy (Canonical\textgreater{}Non-canonical\textgreater{}Crying\textgreater{}Laughing), segments with at least one instance of each judgment were labelled as such:

@@

In this section, we provide descriptive analyses of our dataset. According to lab annotators, 14\% of segments were Canonical, 60\% Non-Canonical, 1\% Laughing, and 4\% Crying, with the remaining 21\% being categorized as \enquote{Don't mark}. Zooniverse data revealed a similar distribution: 15\% Canonical, 60\% Non-Canonical, 3\% Laughing, 7\% Crying, 15\% Junk.
Next, we inspected the relationship between age and child-level derived metrics, of which we had two: i) Linguistic Proportion = (Canonical + Non-Canonical) / All vocalizations (i.e., we remove Junk), and ii) Canonical Proportion = Canonical / (Canonical + Non-Canonical) (i.e., we remove Junk, Crying, and Laughing). Figure 3 shows results of plotting our Proportions against child age. We draw the readers' attention to the fact that the children diagnosed with Angelman syndrome had overall higher levels of Linguistic Proportion than the typically-developing infants, but the opposite was true for Canonical Proportion.

@@

Descriptive analyses on the laboratory annotations showed that correlations between the Linguistic Proportion and age differed across the groups. There was a near-zero relationship among the children diagnosed with Angelman syndrome r(8) = -.091, CI {[}-.682,.571{]}, \emph{p} = .802{]}; and a significant association among low-risk control children r(8) = .7, CI {[}.126,.923{]}, \emph{p} = .024{]}. The Canonical Proportion exhibited non-significant developmental decreases among children diagnosed with Angelman syndrome r(8) = -.393, CI {[}-.82,.314{]}, \emph{p} = .261{]}; and marginal developmental increases among low-risk control r(8) = .516, CI {[}-.168,.865{]}, \emph{p} = .126{]}.

Using the Zooniverse annotations, we found that the association with age was very weak for children diagnosed with Angelman syndrome r(8) = -.174, CI {[}-.724,.512{]}, \emph{p} = .630{]}; whereas low-risk control children showed a significant increase with age r(8) = .629, CI {[}-.001,.902{]}, \emph{p} = .051{]}. Similarly, there were non-significant developmental decreases in the Canonical Proportion among children with Angelman syndrome r(8) = -.407, CI {[}-.825,.299{]}, \emph{p} = .243{]}; and marginal developmental increases among low-risk control children, r(8) = .514, CI {[}-.171,.864{]}, \emph{p} = .129{]}.

@@

These visualizations suggest that performance is moderate to good, which was confirmed via statistical analyses. The overall (weighted) accuracy is 73\%, CI = {[}72,74{]}, kappa is .531, and the Gwet's AC1 coefficient is .682, CI = {[}.669,.694{]}.

@@

Although the classification at the segment level is only moderately accurate, what we are ultimately interested in is whether citizen scientists' classifications are able to provide a reliable snapshot of children's individual development. We illustrate this association in Figure 5. Looking at all 20 children together, we found a strong positive correlation r(18) = .794, CI {[}.543,.915{]}, \emph{p} \textless{} .001{]} between Linguistic Proportion by child from the Zooniverse and the lab annotators' data. When we split by participant group, correlations remain high: for Angelman syndrome r(8) = .878, CI {[}.555,.971{]}, \emph{p} = .001{]}; low-risk control r(8) = .828, CI {[}.415,.958{]}, \emph{p} = .003{]}.

@@

Similarly, a strong positive correlation is found in the Canonical Proportion r(18) = .92, CI {[}.806,.968{]}, \emph{p} \textless{} .001{]}. When we split by participant group, correlations remain high although we do note they are somewhat smaller for the children with Angelman syndrome: r(8) = .681, CI {[}.091,.917{]}, \emph{p} = 0.03{]}; than the low-risk control children r(8) = .984, CI {[}.932,.996{]}, \emph{p} \textless{} .001.

@@

We investigated this hypothesis by calculating the proportion of their data labeled as \enquote{Junk} for each individual child. There was no significant difference in the proportions of their data labeled as \enquote{Junk} for children with Angelman syndrome (M = 0.14) compared to the low-risk group (M = 0.16): Welch's t(13.35) = -0.58, \emph{p} = .569. We therefore collapsed across groups for this exploratory analysis, and split the 20 children using a median split on the proportion of their data labeled as \enquote{Junk}. Results were similar across these two post-hoc subgroups (see Figure 6). For Linguistic Proportion, the correlation across lab and Zooniverse data for the lower Junk group was r(8) = .863, CI {[}.511,.967{]}, \emph{p} = .001{]}; and for the higher Junk group it was r(8) = .895, CI {[}.608,.975{]}, \emph{p} \textless{} .001. For Canonical Proportion, the correlation across lab and Zooniverse data for the lower Junk group was r(8) = .957, CI {[}.824,.99{]}, \emph{p} \textless{} .001{]}; and for the higher Junk group it was r(8) = .895, CI {[}.608,.975{]}, \emph{p} \textless{} .001. Thus, it does not seem that a higher proportion of \enquote{Junk} judgments is an index of low quality data.

@@

As for correlations between Zooniverse- and laboratory-derived metrics (e.g., linguistic proportion as estimated using Zooniverse coding, versus laboratory coding), we observe very similar levels of correlation: Linguistic Proportion overall r(18) = .798, CI {[}.549,.917{]}, \emph{p} \textless{} .001{]} between Linguistic Proportion by child from the Zooniverse and the lab annotators' data. When we split by participant group, correlations remain high: for Angelman syndrome r(8) = .845, CI {[}.46,.963{]}, \emph{p} = .002{]}; low-risk control r(8) = .794, CI {[}.328,.949{]}, \emph{p} = .006{]}. As for Canonical Proportion overall r(18) = .949, CI {[}.873,.98{]}, \emph{p} \textless{} .001; Angelman syndrome: r(8) = .724, CI {[}.173,.93{]}, \emph{p} = .018{]}; low-risk control infants r(8) = .972, CI {[}.881,.993{]}, \emph{p} \textless{} .001.

@@

Next, we looked at whether having more segments from each child may lead to more reliable metrics. We observed a non-significant trend {[}Welch t(17.88)=-0.53{]} for lower number of segments in the Angelman syndrome group (M = 348.70, range 163-599) than among low-risk control infants (M = 375.50, range 224-627), likely because of the lower volubility of the former children. Moreover, these numbers of segments are much larger than those used in previous work relying on citizen science classifications (Cychosz et al., 2019). We therefore asked whether the correlations between laboratory and Zooniverse child-level estimates are affected by how much data is extracted from each child by sampling 100 segments from all children (following Cychosz et al., 2019). We randomly sampled 100 segments from each child's data, and recalculated the Linguistic and Canonical Proportions based only on these associated judgments. We repeated this process 50 times, to assess the extent to which the association between laboratory- and Zooniverse-derived metrics varied in each random sample (e.g., the correlation between Linguistic Proportion as estimated using Zooniverse coding on the one hand, and Linguistic Proportion as estimated using laboratory coding on the other).

The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, especially in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was {[}.442,.893{]}; for the Angelman syndrome group {[}.490,.969{]}; for the low-risk group {[}.289,.989{]}. For Canonical Proportion, the range of correlations found for all infants was {[}.750,.943{]}; for the Angelman syndrome group {[}.790,.994{]}; for the low-risk group {[}.547,.939{]}.

@@

\caption{\label{tab:tab-cors}Pearson correlation coefficients across metrics derived from laboratory and Zooniverse annotations in the Angelman syndrome (AS) group data, low-risk (LR) group data, or for all children together (all) in three ways. First, All seg indicates that Zooniverse annotations at the chunk level were first combined at the segment level. Second, Chunks indicates that they were analyzed directly at the chunk level. Both of these are based on all the data. Third, rows labeled 100 seg indicate that laboratory- and Zooniverse-derived metrics were based on only 100 segments (median over 50 runs in which 100 segments were randomly selected from each child).}
\centering
\begin{tabular}[t]{r|r}
\hline
Linguistic Proportion & Canonical Proportion\\
\hline
0.878 & 0.681\\
\hline
0.828 & 0.984\\
\hline
0.794 & 0.920\\
\hline
\end{tabular}
\end{table}

>>>>

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29 rue d'Ulm, 75005, Paris, France. E-mail: alecristia@gmail.com}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\singlespacing}
\AtBeginEnvironment{lltable}{\singlespacing}
\AtBeginEnvironment{tablenotes}{\singlespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

@@

A large body of research has investigated both fine-grained and coarse descriptions of children's vocalizations as a function of age and diagnosis, and it is beyond the scope of this paper to provide a full summary of this work. Moreover, the way in which vocal development has been studied in the past may not easily translate to long-form recordings. As mentioned earlier, long-form recordings have several advantages, including capturing the child's vocal patterns in their natural environment and being able to accumulate a great amount of data easily, which is particularly useful for diagnoses and pathologies characterized by low levels of vocal production. However, this also means that the audiorecording is harder to process than an audiorecording gathered in more manicured and stable conditions: In a typical daylong recording, the child will sometimes be in a quiet room with just her primary caregiver, but later in a noisy supermarket or having dinner with family and friends. In fact, human annotation of such audio is estimated to take about 30 times the audio length, with these estimates being greater the more precise one wants or needs to be (Casillas et al., 2017). It is for this reason that most users of long-form recordings have turned to automatized software for at least a first-pass analysis.

@@

The following description uses several key concepts: A \enquote{judgment} or \enquote{label} is a single classification provided by a Zooniverse user in response to a single chunk; a \enquote{chunk} is a 500-ms clip extracted from the daylong audio to represent part or all of a segment; a segment is a section of the daylong audio automatically classified as having been uttered by the key child according to the LENA\textsuperscript{TM} algorithm. Bearing this terminology in mind, we provide an overview of the data and how it was processed before the analyses below.

An impressive total of 1,532 individual Zooniverse users provided 169,803 judgments on 33,730 500-ms chunks, corresponding to 11,980 LENA\textsuperscript{TM} segments. For a variety of technical mishaps, 1,158 judgments had to be excluded, leaving 33,729 chunks (from 11,980 LENA\textsuperscript{TM} segments) for which we had five Zooniverse labels (for a total of 168,645 judgments included). Among these 33,729 chunks, 0.18\% had no matching labels, 19.52\% had two matching labels (the threshold used for lab-annotated segments), and 80.30\% had three or more matching labels, or majority agreement within Zooniverse labels. Future work may explore different ways of setting the minimal requirement for convergence, but for further analyses here, we focused on the 80.30\% of chunks that \emph{did} have at least three labels in agreement (i.e., majority agreement). This represented 135,420 labels for 27,084 chunks, corresponding to 11,980 LENA\textsuperscript{TM} segments. Given that each chunk is 500 ms in length, this means about 3.76 hours of audio data were annotated by 8 different annotators (3 in the laboratory, 5 on Zooniverse).

There was one more layer of pre-processing that was necessary for our analyses: Lab annotators provided judgments at the level of LENA\textsuperscript{TM} segments, whereas Zooniverse annotators provided judgments on 500 ms chunks, which are typically smaller than the segments. Therefore, we needed to combine chunk-level judgments to reconstruct segment-level judgments. We did this by considering the majority label extracted from Zooniverse judgments for all chunks associated with each segment, and then following these rules: If the majority label for all chunks associated with a given segment were Junk, then the segment was labelled as Junk; then, following a hierarchy (Canonical\textgreater{}Non-canonical\textgreater{}Crying\textgreater{}Laughing), segments with at least one instance of each judgment were labelled as such:

@@

In this section, we provide descriptive analyses of our dataset. According to lab annotators, 14\% of segments were Canonical, 60\% Non-Canonical, 1\% Laughing, and 4\% Crying, with the remaining 21\% being categorized as \enquote{Don't mark}. Zooniverse data revealed a similar distribution: 15\% Canonical, 60\% Non-Canonical, 3\% Laughing, 8\% Crying, 15\% Junk.
Next, we inspected the relationship between age and child-level derived metrics, of which we had two: i) Linguistic Proportion = (Canonical + Non-Canonical) / All vocalizations (i.e., we remove Junk), and ii) Canonical Proportion = Canonical / (Canonical + Non-Canonical) (i.e., we remove Junk, Crying, and Laughing). Figure 3 shows results of plotting our Proportions against child age. We draw the readers' attention to the fact that the children diagnosed with Angelman syndrome had overall higher levels of Linguistic Proportion than the typically-developing infants, but the opposite was true for Canonical Proportion.

@@

Descriptive analyses on the laboratory annotations showed that correlations between the Linguistic Proportion and age differed across the groups. There was a near-zero relationship among the children diagnosed with Angelman syndrome r(8) = -.092, CI {[}-.682,.571{]}, \emph{p} = .801{]}; and a significant association among low-risk control children r(8) = .7, CI {[}.126,.923{]}, \emph{p} = .024{]}. The Canonical Proportion exhibited non-significant developmental decreases among children diagnosed with Angelman syndrome r(8) = -.393, CI {[}-.82,.315{]}, \emph{p} = .261{]}; and marginal developmental increases among low-risk control r(8) = .516, CI {[}-.169,.865{]}, \emph{p} = .127{]}.

Using the Zooniverse annotations, we found that the association with age was very weak for children diagnosed with Angelman syndrome r(8) = -.179, CI {[}-.727,.508{]}, \emph{p} = .621{]}; whereas low-risk control children showed a significant increase with age r(8) = .632, CI {[}.004,.903{]}, \emph{p} = .050{]}. Similarly, there were non-significant developmental decreases in the Canonical Proportion among children with Angelman syndrome r(8) = -.404, CI {[}-.824,.303{]}, \emph{p} = .248{]}; and marginal developmental increases among low-risk control children, r(8) = .518, CI {[}-.165,.866{]}, \emph{p} = .125{]}.

@@

These visualizations suggest that performance is moderate to good, which was confirmed via statistical analyses. The overall (weighted) accuracy is 73\%, CI = {[}72,74{]}, kappa is .534, and the Gwet's AC1 coefficient is .683, CI = {[}.671,.695{]}.

@@

Although the classification at the segment level is only moderately accurate, what we are ultimately interested in is whether citizen scientists' classifications are able to provide a reliable snapshot of children's individual development. We illustrate this association in Figure 5. Looking at all 20 children together, we found a strong positive correlation r(18) = .8, CI {[}.554,.918{]}, \emph{p} \textless{} .001{]} between Linguistic Proportion by child from the Zooniverse and the lab annotators' data. When we split by participant group, correlations remain high: for Angelman syndrome r(8) = .873, CI {[}.539,.97{]}, \emph{p} = .001{]}; low-risk control r(8) = .831, CI {[}.421,.959{]}, \emph{p} = .003{]}.

@@

Similarly, a strong positive correlation is found in the Canonical Proportion r(18) = .921, CI {[}.807,.969{]}, \emph{p} \textless{} .001{]}. When we split by participant group, correlations remain high although we do note they are somewhat smaller for the children with Angelman syndrome: r(8) = .681, CI {[}.089,.917{]}, \emph{p} = 0.03{]}; than the low-risk control children r(8) = .985, CI {[}.937,.997{]}, \emph{p} \textless{} .001.

@@

We investigated this hypothesis by calculating the proportion of their data labeled as \enquote{Junk} for each individual child. There was no significant difference in the proportions of their data labeled as \enquote{Junk} for children with Angelman syndrome (M = 0.14) compared to the low-risk group (M = 0.17): Welch's t(13.33) = -0.56, \emph{p} = .588. We therefore collapsed across groups for this exploratory analysis, and split the 20 children using a median split on the proportion of their data labeled as \enquote{Junk}. Results were similar across these two post-hoc subgroups (see Figure 6). For Linguistic Proportion, the correlation across lab and Zooniverse data for the lower Junk group was r(8) = .866, CI {[}.521,.968{]}, \emph{p} = .001{]}; and for the higher Junk group it was r(8) = .893, CI {[}.603,.975{]}, \emph{p} \textless{} .001. For Canonical Proportion, the correlation across lab and Zooniverse data for the lower Junk group was r(8) = .958, CI {[}.827,.99{]}, \emph{p} \textless{} .001{]}; and for the higher Junk group it was r(8) = .896, CI {[}.61,.975{]}, \emph{p} \textless{} .001. Thus, it does not seem that a higher proportion of \enquote{Junk} judgments is an index of low quality data.

@@

As for correlations between Zooniverse- and laboratory-derived metrics (e.g., linguistic proportion as estimated using Zooniverse coding, versus laboratory coding), we observe very similar levels of correlation: Linguistic Proportion overall r(18) = .798, CI {[}.549,.917{]}, \emph{p} \textless{} .001{]} between Linguistic Proportion by child from the Zooniverse and the lab annotators' data. When we split by participant group, correlations remain high: for Angelman syndrome r(8) = .845, CI {[}.46,.963{]}, \emph{p} = .002{]}; low-risk control r(8) = .794, CI {[}.328,.949{]}, \emph{p} = .006{]}. As for Canonical Proportion overall r(18) = .949, CI {[}.873,.98{]}, \emph{p} \textless{} .001; Angelman syndrome: r(8) = .724, CI {[}.173,.93{]}, \emph{p} = .018{]}; low-risk control infants r(8) = .971, CI {[}.88,.993{]}, \emph{p} \textless{} .001.

@@

Next, we looked at whether having more segments from each child may lead to more reliable metrics. We observed a non-significant trend {[}Welch t(17.88)=-0.53{]} for lower number of segments in the Angelman syndrome group (M = 348.40, range 163-599) than among low-risk control infants (M = 375.30, range 224-627), likely because of the lower volubility of the former children. Moreover, these numbers of segments are much larger than those used in previous work relying on citizen science classifications (Cychosz et al., 2019). We therefore asked whether the correlations between laboratory and Zooniverse child-level estimates are affected by how much data is extracted from each child by sampling 100 segments from all children (following Cychosz et al., 2019). We randomly sampled 100 segments from each child's data, and recalculated the Linguistic and Canonical Proportions based only on these associated judgments. We repeated this process 50 times, to assess the extent to which the association between laboratory- and Zooniverse-derived metrics varied in each random sample (e.g., the correlation between Linguistic Proportion as estimated using Zooniverse coding on the one hand, and Linguistic Proportion as estimated using laboratory coding on the other).

The mean correlations across 50 runs were lower than those recovered using all segments from each child (see Table 2), particularly for the low-risk younger infants, and for Linguistic Proportion. This may indicate that, especially in some groups of infants, 100 segments may not be sufficient to capture a stable estimate of the child's Linguistic and Canonical Proportions. We also observed quite a bit of variance across the 50 runs. For Linguistic Proportion, the range of correlations found for all infants was {[}.614,.877{]}; for the Angelman syndrome group {[}.426,.951{]}; for the low-risk group {[}.637,.937{]}. For Canonical Proportion, the range of correlations found for all infants was {[}.776,.955{]}; for the Angelman syndrome group {[}-.063,.915{]}; for the low-risk group {[}.868,.991{]}.

@@

\caption{\label{tab:tab-cors}Pearson correlation coefficients across metrics derived from laboratory and Zooniverse annotations in the Angelman syndrome (AS) group data, low-risk (LR) group data, or for all children together (all) in three ways. First, All seg indicates that Zooniverse annotations at the chunk level were first combined at the segment level. Second, Chunks indicates that they were analyzed directly at the chunk level. Both of these are based on all the data. Third, rows labeled 100 seg indicate that laboratory- and Zooniverse-derived metrics were based on only 100 segments (median over 50 runs in which 100 segments were randomly selected from each child).}
\centering
\begin{tabular}[t]{r|r}
\hline
Linguistic Proportion & Canonical Proportion\\
\hline
0.873 & 0.681\\
\hline
0.831 & 0.985\\
\hline
0.800 & 0.921\\
\hline
\end{tabular}
\end{table}
